\pkg{cubble}: An R Package for Structuring Spatio-temporal Data

### 2022-01-31 4-5-interactive.Rmd
update the interactive linking figure

```{r interactive-linking, echo = FALSE, out.width="100%", out.height="20%", fig.retina = 2, dpi = 300, fig.cap = "Exploring temperature variation using linkning of a map and seasonal display. Each row is a screen dump of the process. The top row shows all locations and all temperature profiels. Selecting a location with high variance on the map produces the plot in the second row. The maximum nad minimum temperature is shown using a ribbon.", fig.show='hold'}
knitr::include_graphics(here::here("figures/linking.png"))
knitr::include_graphics(here::here("figures/linking-north.png"))
knitr::include_graphics(here::here("figures/linking-mid.png"))
knitr::include_graphics(here::here("figures/linking-south.png"))
```

>>>>

```{r interactive-linking, echo = FALSE, out.width="100%", out.height="23%", fig.retina = 2, dpi = 300, fig.cap = "Exploring temperature variation using linking of a map and seasonal display. Each row is a screen dump of the process. The top row shows all locations and all temperature profiles. Selecting a location with high variance on the map produces the plot in the second row. The maximum nad minimum temperature is shown using a ribbon. The bottom row first selects the lowest temperature in Auguest in the seasonal display. A location in the Tasmania Island is then selected and surprisingly, it is actually warmer than the Thredbo AWS.", fig.show='hold'}
knitr::include_graphics(here::here("figures/linking.png"))
knitr::include_graphics(here::here("figures/linking-north.png"))
knitr::include_graphics(here::here("figures/linking-lower.png"))
#knitr::include_graphics(here::here("figures/linking-south.png"))
```

### 2022-01-31 main.tex
update the interactive linking figure

{\centering \includegraphics[width=1\linewidth,height=0.2\textheight]{/Users/sherryzhang/Documents/research/paper-cubble/figures/linking} \includegraphics[width=1\linewidth,height=0.2\textheight]{/Users/sherryzhang/Documents/research/paper-cubble/figures/linking-north} \includegraphics[width=1\linewidth,height=0.2\textheight]{/Users/sherryzhang/Documents/research/paper-cubble/figures/linking-mid} \includegraphics[width=1\linewidth,height=0.2\textheight]{/Users/sherryzhang/Documents/research/paper-cubble/figures/linking-south}

@@

\caption[Exploring temperature variation using linkning of a map and seasonal display]{Exploring temperature variation using linkning of a map and seasonal display. Each row is a screen dump of the process. The top row shows all locations and all temperature profiels. Selecting a location with high variance on the map produces the plot in the second row. The maximum nad minimum temperature is shown using a ribbon.}\label{fig:interactive-linking}
\end{figure}
\end{CodeChunk}

>>>>

{\centering \includegraphics[width=1\linewidth,height=0.23\textheight]{/Users/sherryzhang/Documents/research/paper-cubble/figures/linking} \includegraphics[width=1\linewidth,height=0.23\textheight]{/Users/sherryzhang/Documents/research/paper-cubble/figures/linking-north} \includegraphics[width=1\linewidth,height=0.23\textheight]{/Users/sherryzhang/Documents/research/paper-cubble/figures/linking-lower}

@@

\caption[Exploring temperature variation using linking of a map and seasonal display]{Exploring temperature variation using linking of a map and seasonal display. Each row is a screen dump of the process. The top row shows all locations and all temperature profiles. Selecting a location with high variance on the map produces the plot in the second row. The maximum nad minimum temperature is shown using a ribbon. The bottom row first selects the lowest temperature in Auguest in the seasonal display. A location in the Tasmania Island is then selected and surprisingly, it is actually warmer than the Thredbo AWS.}\label{fig:interactive-linking}
\end{figure}
\end{CodeChunk}
